---
title: "Checking out Broom Vignette"
author: "Hamish Spalding"
date: "31/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("pacman")
pacman::p_load(tidyverse)
```


## Intro to Broom

Following Intro to Broom at this link:
<https://cran.r-project.org/web/packages/broom/vignettes/broom.html>

**broom** package description is that "broom Converts Statistical Nalysis Objects into TIdy Tibbles."  

**broom use**s mpg data, so maybe try follow example with wome some different data. Iris is too common.   

```{r}
#Get some data from here - requires registration
#https://opendata.transport.nsw.gov.au/dataset/train-occupancy-nov-2016-feb-2017

```


#Get some data from here - requires registration  

https://opendata.transport.nsw.gov.au/dataset/train-occupancy-nov-2016-feb-2017

upload .csv to R and then spark

```{r}
pacman::p_load(SparkR,SparkR)

SparkR::sparkR.session() # https://docs.databricks.com/spark/latest/sparkr/rstudio.html#get-started-with-rstudio-server-open-source
library(sparklyr)
sc <- spark_connect(method = "databricks")
src_tbls(sc)

TrainOccupancyFeb2017 <- readr::read_csv("Train Occupancy - Feb 2017.csv", # C:\Users\hspalding\Downloads\Train Occupancy - Feb 2017
                                         col_types = cols(                 # need to save above file - too large for github - 1.1m rows..
                                           day = col_double(),
                                           Actual.Stop.Station = col_character(),
                                           Actual.Station.Arrv.Time = col_datetime(format = ""),
                                           Actual.Station.Dprt.Time = col_datetime(format = ""),
                                           Segment.Direction = col_character(),
                                           Trip.Name = col_character(),
                                           Service.Line = col_character(),
                                           Orig..Station = col_character(),
                                           Dest..Station = col_character(),
                                           Leading.Set.Type = col_character(),
                                           Node.Seq.Order = col_double(),
                                           Actual.Station.Dprt.Time.Band = col_character(),
                                           `Occupancy Status` = col_character(),
                                           `Occupancy Range` = col_character())
)
                                        
src_tbls(sc)
sparklyr::copy_to(sc, TrainOccupancyFeb2017)
#sparklyr::sdf_copy_to(sc,TrainOccupancyFeb2017, overwrite = TRUE)

# create a reference to the spark data TrainOccupancyFeb2017_csv using the dplyr::tbl() function
TrainOccupancyFeb2017_csv_tbl <- dplyr::tbl(sc,"TrainOccupancyFeb2017")

```

```{r}
TrainOccupancyFeb2017 %>% tally()

origin <- unique(TrainOccupancyFeb2017$Orig..Station)
origin.df <- as.data.frame(origin,col.names =c("station"))

str(origin.df)



dest <- unique(TrainOccupancyFeb2017$Dest..Station)
dest.df <- as.data.frame(col.names =c("station"),dest)

origin <-list(c("station"),origin)
dest <-list(c("station"),dest)

as.data.frame()
comb <-list(origin, dest)

as.data.frame(col.names =c("station"),origin)

bind_rows(origin,dest) %>% tibble("stations")
?bind_rows()


```

## get some BOM data

```{r}
if (!require("remotes")) {
  install.packages("remotes", repos = "http://cran.rstudio.com/")
  library("remotes")
}

install_github("ropensci/bomrang", build_vignettes = TRUE)

library(bomrang)
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
